Scheeper's Meager-NWD Game and the Menger Game

### 2014-06-04 phd/dissertation/chapter3.tex
minor work on confinality case

\begin{prop}
  $\pl F\win\pfgame\kappa$ for all cardinals $\kappa$.
\end{prop}

@@

TODO:

@@

>>>>

@@

We aim to show that $\pl F \not\codewin \pfgame\kappa$ for all
$\kappa$.

@@

\begin{proof}
Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
$W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.

Define
  \[
    \sigma(\<N,W\>)
      =
    N
      \cup
    (|N|+1)
      \cup
    \{\alpha_W\}
      \cup
    \bigcup_{\alpha \in N} f(\alpha) \restriction |N|
  \]

Consider the play $\left<\emptyset,W_0,N_1,W_1,N_2,W_2,\dots\right>$ with $F$ following the strategy $\sigma$. Let $\gamma \in W_i$, and note $\gamma \in f(\alpha_{W_i})$ (and $\gamma \in f(\alpha_{W_i})\restriction |N_n|$ for sufficiently large $n$). \[N_{i+1} = \sigma(N_i,W_i) \supseteq \{\alpha_{W_i}\}\] and thus \[N_{n+1} = \sigma(N_n,W_n) \supseteq \bigcup_{\alpha \in N_n} f(\alpha) \restriction |N_n| \supseteq \bigcup_{\alpha \in N_{i+1}} f(\alpha) \restriction |N_n| \supseteq f(\alpha_{W_i}) \restriction |N_n|\] showing $\gamma \in N_{n+1}$. Since $\gamma$ is forbidden in round $n+1$, $\gamma$ appears in finitely many sets chosen by $C$.

We turn our attention to $Con_{O,P}(\Sigma\mathbb{R}^\kappa)$. We define the winning strategy $\tau(U,p)$ for $O$ as follows: let $N(U)$ be the non-$\mathbb{R}$ coordinates in the basic open set $U$ and $W(p)$ be the non-$0$ coordinates in $p$. Then $\tau(U,p) = \left(\prod_{\alpha<\kappa} U_\alpha\right) \cap \Sigma\mathbb{R}^\kappa$ where if $\alpha \in \sigma(N(U),W(p))$ then $U_\alpha = (-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and $U_\alpha=\mathbb{R}$ otherwise.

Consider the play $\left<\emptyset,p_0,U_1,p_1,U_2,p_2,\dots\right>$ with $O$ following the strategy $\tau$. Observe that $N(\tau(U,p))=\sigma(N(U),W(p))$. Thus $p_i(\gamma)\not=0$ is equivalent to $\gamma \in W(p_i)$, and by the above argument, for sufficiently large $n$, $\gamma \in \sigma(N(U_n),W(p_n))$. Therefore from round $n$ onward the $\gamma$-coordinates of points chosen by $P$ must lay in $(-\frac{1}{|N(U)|},\frac{1}{|N(U)|})$ and converge to $0$.
\end{proof}
